Setting up Data

### 2019-12-20 doc/Main_Report_Results.rmd
working on the chrm class proportions sections, other small edits

@@

Details of dataset cleaning ect is in SetupData.rmd

Effects from different factors are reviewed in Effects.Rmd

@@

The data below are from hand measured cells (not from bivalent data)
generate smaller data set of chrm proportions (0CO, 1CO,2CO etc)
10 cells from each musc category. **Add Molf male**

ToDo -- add more hand curated data for the bivalent proportions

```{r chrm_prop_data, echo=FALSE, eval=FALSE}
#shut off eval for now because of wd / path error
#chrm.class.DF = read.csv("~./MLH1repo/data/ChrmClassProportions.csv", header = TRUE)

@@

#summarize by category
proportion_stats_category  <- ddply(.data=chrm.class.DF[chrm.class.DF$sex == "male",], 
                 .(category),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                  tot_biv  = sum(biv.sum.check),

                 n0CO = sum(n0CO),
                  n1CO = sum(n1CO),
                  n2CO = sum(n2CO),
                  n3CO = sum(n3CO),
                  n4CO = sum(n4CO),

@@

)
#str(this_thing2)

#this first one is the 'first' MLH1 count
oopp2 <- lm( mean.MLH1.foci2 ~ per0CO+ per1CO +per2CO +per3CO, data = proportion_stats_category)
#summary(oopp2)
#none of the classes are significant

#mean is the new calculated-- mean 0CO is significant and intercept
oopp <-  lm( mean.MLH1.foci ~ per0CO+ per1CO +per2CO +per3CO, data = proportion_stats_category)
#summary(oopp)
#not sure if these are inter-correlated
#I don't know why 0COs and the intercept are significant..
#0CO and 1CO are significant when only chrm classes are included (and intercept)

@@

#melt.table = read.csv("~./MLH1repo/data/ChrmClassProportions_melt.csv", header = TRUE)
melt.table$fileName <- (melt.table$Original.Name)

#melt.table <- add_mouse(melt.table)
#melt.table <- add_strain(melt.table)
#melt.table <- add_sex(melt.table)
#melt.table <- add_category(melt.table)

melt.table$strain<- factor(melt.table$strain,levels =c("LEW",
                      "WSB","G", "TOM","AST","KAZ", "SKIVE","PWD","MSM"), order=T )

melt.table <- with(melt.table, melt.table[order(strain),])

other_thing <- ggplot(data = melt.table, aes(y = value, x = strain, fill=as.factor(type)) ) + geom_col(position = "dodge")+facet_grid(sex~subsp, scales = "free")+ggtitle("Chrm Proportions from Hand Measured")+ylim(c(0,1))

other_thing

@@

@@

@@

>>>>

load in more Data, chrm proportions, total SC,
write / standardize the data set up for those

@@

Details of dataset cleaning ect is in SetupData.rmd
Effects from different factors are reviewed in Effects.Rmd

@@

The data below are from hand measured cells (not from bivalent data)
generate smaller data set of chrm proportions (0CO, 1CO,2CO etc)
10 cells from each musc category. **Add Molf female**

```{r chrm_prop_data, echo=FALSE}
#shut off eval for now because of wd / path error
#chrm.class.DF = read.csv("~./MLH1repo/data/ChrmClassProportions.csv", header = TRUE)
#chrm.class.DF = read.csv("C:/Users/alpeterson7/Documents/MLH1repo/data/ChrmClassProportions.csv", header = TRUE)

chrm.class.DF = read.csv("C:/Users/alpeterson7/Documents/MLH1repo/data/ChrmClassProportions2.csv", header = TRUE)

#this excel file is ~100 cells (10 per category) where I manually verified the number of chrom classes. (this file can also be used to quantify error for CO counts)

@@

#summarize by category
proportion_stats_category  <- ddply(.data=chrm.class.DF, 
                 .(category),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                  tot_biv  = sum(biv.sum.check,  na.rm = TRUE),

                 n0CO = sum(n0CO, na.rm = TRUE),
                  n1CO = sum(n1CO,na.rm = TRUE),
                  n2CO = sum(n2CO,na.rm = TRUE),
                  n3CO = sum(n3CO,na.rm = TRUE),
                  n4CO = sum(n4CO,na.rm = TRUE),

@@

)
#this is the table that needs melting
#but is also easy to redo by hand

#write.table(proportion_stats_category, "~./MLH1repo/prop_category.csv", sep=",", row.names = FALSE)
```

```{r plot.chrm.prop.melt, echo=FALSE}

#add subspecies to these values
melt.Chrm.Prop.table = read.csv("~./MLH1repo/data/ChrmClassProportions2_melt.csv", header = TRUE)
melt.Chrm.Prop.table <- melt.Chrm.Prop.table[c(1:5)]

#add the subsps

melt.Chrm.Prop.table$strain<- factor(melt.Chrm.Prop.table$strain, levels =c("LEW",
                      "WSB","G", "TOM","AST","KAZ", "SKIVE","PWD","MSM", "MOLF"), order=T )

melt.Chrm.Prop.table <- with(melt.Chrm.Prop.table, melt.Chrm.Prop.table[order(strain),])

chrm.class.barplot <- ggplot(data = melt.Chrm.Prop.table, aes(y = value, x = strain, fill=as.factor(type)) ) + geom_col(position = "dodge")+facet_grid(sex~strain, scales = "free")+ggtitle("Chrm Proportions from Hand Measured")+ylim(c(0,1))

#need a second DF / the first df
#+ annotate() text 
#annotate()text

#proportion_stats_category,  tot_biv, ncells

#add number of cells and bivalents in the corner

chrm.class.barplot
```

```{r test.Chrm.Prop, echo=FALSE}

#this first one is the 'first' MLH1 count
#which is this variable

#oopp2 <- lm( mean.MLH1.foci2 ~ per0CO+ per1CO +per2CO +per3CO, data = proportion_stats_category)
#summary(oopp2)
#none of the classes are significant

#mean is the new calculated-- mean 0CO is significant and intercept
#oopp <-  lm( mean.MLH1.foci ~ per0CO+ per1CO +per2CO +per3CO, data = #proportion_stats_category)

#summary(oopp)
#not sure if these are inter-correlated
#I don't know why 0COs and the intercept are significant..
#0CO and 1CO are significant when only chrm classes are included (and intercept)

@@

#Need to run the chrm proportions thru melt code.

@@

Add p.values of tests for the how the proportions differ.

@@

#this is a second mode of

@@

make the heterochiasmy plot, with female strain averages adjusted for X
(measure variance in CO counts for the top 5 female whole cell bivalents)
(variance in )
how does this compare to variance of mid 5, bottom 5?

### 2019-12-20 src/SetupData.Rmd
working on the chrm class proportions sections, other small edits

```{r save.RData, echo=FALSE}
save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_12.3.19.RData")
#  OutPut: big large MLH1_data (AP's) df, big DF of BD with just the mice I want.
#  MLH1_data_table, means and variance of AP and BD MLH1 values. made from seperate tables from AP and BD data.
#  make sure decimal places are consistant

>>>>

```{r save.RData, echo=FALSE}

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_12.20.19.RData")

#  OutPut: big large MLH1_data (AP's) df, big DF of BD with just the mice I want.
#  MLH1_data_table, means and variance of AP and BD MLH1 values. made from seperate tables from AP and BD data.
#  make sure decimal places are consistant
